### 2013-02-17 article/link-prediction.tex
article first commit

\newcommand{\score}[1]{{\mathrm {#1}}}

\section{Link Predicton}

Link prediction in a classic and well-studied problem over social
networks, e.g.~\cite{}. Formally, the {\em link prediction problem\/}
is: Given a snapshot of a social network at a given point in time,
predict which edges will be added to the network as it naturally
evolves. The ability to predict such links is considered important for
friend recommendation, i.e., as predicted links are likely to
represent natural relationships in the network. Link prediction is
also useful for inferring missing links, i.e., discovering which links
are surprisingly missing (and then the social process leading to this
formation can be further analyzed).

Many score functions have been developed for predicting links. In general, a
a score function is defined over pairs of nodes, and indicates
the likelihood of a link forming between these nodes. As of now, no
clear winner for the link prediction problem has been found. Instead,
different score functions have proven useful over varying datasets. As we will
see later, score functions may differ substantionally in their ease of
implementation and in their efficiency.

Below we detail the score functions considered in this paper. These particular
functions were chosen for two reasons. First, they are  the
``bread-and-butter'' of link prediction, i.e., they are
widely considered and studied. Second, their implementation requires a
variety of types of accesses to the social network graph (only to
neighbors, iterating over paths or random walks). Hence, they can
perhaps shed light on how efficient other common graph operations
would be over social networks (in different system implementations).

In total, we considered seven score functions for link prediction. In the
following, we assume that $x$ and $y$ are nodes in a social
network. We use $N(x)$ to denote the set of all neighbors of
$x$. Finally, we
use $P^l(x,y)$ to denote the set of all paths of length $l$ between $x$
and $y$.
\begin{itemize}
\item {\bf Common neighbors:} The common neighbors $\score{cneigh}$
  function measures the number of neighbors in common to $x$ and $y$,
  i.e., \[ \score{cneigh}(x,y) = |N(x) \cap N(y)| \,.\]
\item {\bf Jaccard coefficient:} The Jaccard coefficient is slightly
  more sophisticated than common neighbors, as it also takes into
  considering the total number of neighbors that $x$ and $y$
  have. This is significant, since nodes with many neighbors are more
  likely to have neighbors in common. Formally, the Jaccard
  coefficient is defined as
\[ \score{jacc}(x,y) = \frac{|N(x) \cap N(y)|}{|N(x) \cup N(y)|}\,.\]
\item {\bf Adamic-Adar:} The Adamic-Adar measure~\cite{} considers
  nodes to be related if they have common neighbors, but weights the
  importance of a common neighbor $z$ proportionately to the number of
  neighbors of $z$. This gives more weight to rarer common neighbors,
  i.e., to nodes $z$ that have few neighbors themselves, as follows
\[ \score{aa}(x,y) = \sum_{z\in N(x)\cap N(y)} \frac{1}{\log{|N(z)|}}\,.\]
\item {\bf Preferential attachment:} In this score function, popular
  nodes (i.e., those with many neighbors) are considered more likely
  to form relationships one with another
\[ \score{pref}(x,y) = |N(x)|\times |N(y)|\,.\]
\item {\bf Graph distance:} Unlike all previous measures, that only
  directly considered the neighbors of $x$ and $y$, graph distance
  takes into consideration the relationship between nodes that may be
  far away. Thus, this scoring function $\score{dist}(x,y)$ is simply the
  the length of the shortest path between  $x$ and $y$. 
\item {\bf Katz measure:} The Katz measure~\cite{} takes into
  consideration all paths between $x$ and $y$, but these paths are
  weighted by their length. In general, $\score{katz}$ is computed as
\[ \score{katz}(x,y) = \sum_{l=1}^\infty \beta^l |P^l(x,y)|\,,\]
where $0<\beta<1$. We used a $\beta$ value of 0.1. For efficiency
purposes, we only summed until paths 
of length 3.
\item {\bf Rooted PageRank:} PageRank~\cite{} computes a general importance
  value for a node by measuring the stationary distribution weight of
  a node $x$ under a random walk, where with probability $\alpha$ one
  jumps to a random node in the graph, while with probability
  $1-\alpha$ one goes to a random neighbor of the current node. Rooted
  PageRank adapts this measure to compute the importance of a node $y$
  with relationship to a node $x$. Thus, $\score{rPR}(x,y)$ computes
  the stationary distribution weight of   a node $y$ under a random
  walk, where with probability $\alpha$ one jumps back to $x$, while
  with probability $1-\alpha$, one proceeds as before (i.e., to a
  random neighbor). In our implementation we chose $\alpha$ \footnote{Sara: rename alpha to d? (damping factor)} as
  0.85 \footnote{Sara: for the damping factor value, should we cite? http://infolab.stanford.edu/pub/papers/google.pdf} 
\end{itemize}
Note that for all measures other than graph distance, a
higher value for the scoring function indicates greater likelihood of
link formation, while for graph distance, the opposite is
true.

### 2013-02-17 article/paper.tex
article first commit

\section{Introduction}
The best paper in the world is~\cite{Liben-Nowell:2003:LPP:956863.956972}.

\input link-prediction

\section{Implementation}
The selected algorithms were implemented and tested over three different 
database systems: Relational, Key-Value store and Graph. 
In each system we attempted to implement the algorithms as natively as possible, 
using that system's features and applying common optimizations.

For the bechmarking we chose MySQL, Redis and Neo4J.
These databases are all open-source, enabling us to publish these benchmarks,
and popular in their domain, therefore considered as a viable option for such social network implementation.

\subsection{MySQL}
MySQL is a popular multi-platform, open-source relational database management
system, sponsored by Oracle. It can be used in client-server or embedded
architecture and it's main features include: 
\begin{itemize}
	\item {\bf Pluggable storage-engines:} MySQL supports several storage engines, 
		most notables are MyISM (fast, simple, no ACID support, no foreign keys) and
		InnoDB (default, supports transactions, ACID and foreign keys).
	\item {\bf Stored Procedures} Like most other relational databases MySQL supports 
		stored procedures execution. Advantages of this feature include 
		avoidance of network traffic for the SQL queries and intermediate results,
		and encapsulation of a multi-query logic in one place.
	\item {\bf Fast Bulk Data Loading} MySQL support very fast data loading from file,
		with it's 'LOAD DATA' statement. From all the systems we tested, this offered 
		the easiest and fastest to load our graph.
\end{itemize}

In this case, the algorithms were implemented as a SQL stored-procedures only,
using indices and intermediate tables when possible. A Python script was used
to run these stored-procedures and collect the benchmarks. For a storage-engine 
we chose InnoDB, the default engine in MySQL 5.5, as it out-performs MyISM in 
most senarios. \footnote{Sara: can we cite Oracle white papers? http://www.oracle.com/partners/en/knowledge-zone/mysql-5-5-innodb-myisam-522945.pdf}

\subsection{Redis}
Redis is an open-source, in-memory key-value store database system, sponsored
by VMware. It's main features are atomic operations, data structure as value
(hash, list, set and sorted-set), optional persistence, pub/sub mechanism,
built-in Lua interpreter and master-slave replication.

Here, some of the algorithms were implemented in Python using redis API, and
some were implemented as Lua scripts (to minimize Redis API calls). When an
index was needed, we simply used another Redis DB (you get 16 with the default
configuration). 
The graphs were represented using adjacency lists, i.e. a key is a node-id and
it's value is a set of his neighbors. That implementation posed a limitation,
since we couldn't store nodes without neighbors, as redis doesn't allow to
store empty sets. \#TODO: why doesn't it matter in our case

\subsection{Neo4J}
Neo4J is a multi-platform, open-source, graph database supported by Neo
Technology. It features full ACID transactions, expressive graph query
language, indexing and high availability. It can operate in an embedded or
client-server architecture.

In this database, we attempted to use only Neo4j's declarative query language
(Cypher) to implement the algorithms, and the client-server architecture to run
them with. The benchmarking was performed using the Python API, which also
assisted in implementing some multi-query algorithms. We found that the best
way to load the graph into Neo4J was to use the BatchInserter class in the
embedded architecture, and copy the created files into the server.

There are some limitations to the Cypher language users should be aware of:
\begin{itemize}
\item There are not many built in functions (e.g. no Power, Log, or Rand
  functions) 
\item No support for user defined functions
\item Queries are really slow when matching a non-trivial pattern over the whole
graph (e.g. common neighbors)  
\end{itemize}

\section{Experiments}
We benchmarked the above implementations using 10 undirected graphs:
\begin{itemize}
\item Three graphs were extracted from the DBLP XML records using the authors as
nodes, and co-authorship relation as edges. Each graph was over a different
time period, and  we only kept authors with 3 or more publication within the
selected time period (core-3).

\item Seven graphs from the Stanford Network Analysis Project (SNAP) dataset
  collection. No changes were made to these graphs.
\end{itemize}

Graphs to add:
\begin{enumerate}
\item Top N index generation (significantly faster on MySQL)
\item Graph Distance (significantly faster on Redis)
\item Jaccard Coefficient (faster on Neo4J)
\end{enumerate}

\section{Conclusions}
The main conclusion we took from this experience is that there is no silver-bullet for storing and running algorithms over social-network graphs. Generally speaking, MySQL seems to have an edge with indices-based implementation, Redis seems to be extremely flexible and open to endless optimization, and Neo4J's Cypher is leading with implementation simplicity.
If we were to build a social network database we'd consider holding replicas in server types of system. While this solution might not be disk-space efficient, it'll provide us the opportunity to achieve the fastest query time with minimal time investment.

Please note that we didn't use any scale out features. A large network implementation can't pick a solution which doesn't have it. \#TODO

### 2013-02-18 article/paper.tex
started adding mysql implementation details

@@
 we chose InnoDB, the default engine in MySQL 5.5, as it out-performs MyISM in 
-most senarios. \footnote{Sara: can we cite Oracle white papers? http://www.oracle.com/partners/en/knowledge-zone/mysql-5-5-innodb-myisam-522945.pdf}
+most senarios. \footnote{Sara: can we cite Oracle white papers? 
+http://www.oracle.com/partners/en/knowledge-zone/mysql-5-5-innodb-myisam-522945.pdf}
+\linebreak
+Implementation details:
+\begin{itemize}
+	\item {\bf Helper Tables} We generated the following helper tables 
+		to speed up some algorithms:
+		\begin{itemize}
+			\item {common-neighbors (id1, id2, neighbor)}
+			\item {common-neighbors-count (id1, id2, number of common neighbors)}
+			\item {neighbors (id, number of neighbors)}
+			\item {topN (id, number of neighbors)}
+				This table is simply the top 101 items of the neighbors table.
+		\end{itemize}
+	\item {\bf Common Neighbors (global)} 
+		To find the top N records with most common neighbors, 
+		we selected them from the common-neighbors-count table.
+	\item {\bf Jaccard's Coefficient (global)} 
+		We used the following relation between the cardinality of union and intersection:
+		\[{|N(x) \cup N(y)|} = {|N(x)| + |N(y)| - |N(x) \cap N(y)|}\]
+		So to calculate the score we used the common-neighbors-count and the neighbors helper tables.
+	\item {\bf Adamic/Adar (global)} 
+\end{itemize}
 

### 2013-02-18 benchmark_mysql.py
bug fix in Rooted PageRank. due to precision issues- converging on 10 and looping on 100

@@ -47,7 +47,7 @@ def main():
 	ret["xPreferentialAttachment"] = randomLoopBenchmark(db, "x_Preferential_attachment", 1000)
 	ret["xGraphDistance"] = randomLoopBenchmark(db, "x_Graph_Distance", 1000, [4,100])
 	ret["xKatz"] = randomLoopBenchmark(db, "x_Katz", 100, [3,0.1,100])
-	ret["xRootedPageRank"] = randomLoopBenchmark(db, "x_RootedPageRank", 10)
+	ret["xRootedPageRank"] = randomLoopBenchmark(db, "x_RootedPageRank", 100)
 
 	print(json.dumps(ret))
 

### 2013-02-18 benchmark_neo4j.py

@@ -101,7 +101,7 @@ pGraphNIDtoNeoNodeID = 'start n=node(*) where has(n.nid) and n.nid = %s return n
 pGetNID = "start a=node({n}) return a.nid"
 xRootedPageRankInit = "start n=node(*) where has(n.nid) set n.rpr = %0.16f"
 xRootedPageRankSetSource = "start x=node({n}) match (x)-[:COAUTH]->(y) with (1-%f)+%f*sum(y.rpr/y.neighbors) as nrpr,x set x.nrpr=nrpr"
-xRootedPageRankSetOther = "start x=node(*) where has(x.nid) with x match (x)-[:COAUTH]->(y) where x.nid < y.nid and x.nid <> %d with %f*sum(y.rpr/y.neighbors) as nrpr,x set x.nrpr=nrpr"
+xRootedPageRankSetOther = "start x=node(*) where has(x.nid) with x match (x)-[:COAUTH]->(y) where x.nid <> %d with %f*sum(y.rpr/y.neighbors) as nrpr,x set x.nrpr=nrpr"
 xRootedPageRankSwitch = "start n=node(*) where has (n.nrpr) set n.rpr = n.nrpr"
 xRootedPageRankQueryTop = "start y=node(*) where has(y.rpr) and y.nid <> %d return y.nid, y.rpr order by y.rpr desc limit %d"
 
@@ -203,7 +203,7 @@ def tRootedPageRank(graph_db, params):
 		cypher.execute(graph_db, xRootedPageRankSetSource % (d,d), params)
 		cypher.execute(graph_db, xRootedPageRankSetOther %(xnid,d))
 		cypher.execute(graph_db, xRootedPageRankSwitch)
-		ret, meta = cypher.execute(graph_db, xRootedPageRankQueryTop % (xnid,100))
+		ret, meta = cypher.execute(graph_db, xRootedPageRankQueryTop % (xnid,10))
 		cret = [nid for nid,score in ret]
 
 def main():
@@ -222,7 +222,7 @@ def main():
 	ret["xGraphDistance"] =  randomLoopBenchmark(graph_db, tGraphDistance, dataset, 1000)
 	ret["xPreferentialAttachment"] =  randomLoopBenchmark(graph_db, xPreferentialAttachment, dataset, 1000)
 	ret["xKatz"] =  randomLoopBenchmark(graph_db, tKatz, dataset, 100)
[…]

### 2013-02-18 benchmark_redis.py

@@ -572,7 +572,7 @@ def main():
 	ret["xKatz"] = benchmarkFunctionLoop(x_Katz_Lua, 
 			100, args.dataset, {'redis_interface': rajl, 'limit': 100, 'beta': 0.1, 'max_depth': 3})
 	ret["xRootedPageRank"] = benchmarkFunctionLoop(x_RootedPageRank, 
-			10, args.dataset, {'redis_interface': rajl, 'limit': 100, 'nodes_db': rnodes})
+			100, args.dataset, {'redis_interface': rajl, 'limit': 10, 'nodes_db': rnodes})
 
 	print(json.dumps(ret))
 

### 2013-02-19 article/paper.tex
more implementation details

@@
 	\item {\bf Adamic/Adar (global)} 
+		We used the common-neighbors joined with the neighbors helper table.
+	\item {\bf Preferential attachment (Global)}
+		We used only the topN helper table, because the highest products 
+		must be combinations of the nodes with most neighbors.
+	\item {\bf Common Neighbors (for node)}
+		We used a simple join on the edges table, no helper tables required.
+	\item {\bf Jaccard's Coefficient (for node)}
+		We used the relation between the cardinality of union and intersection,
+		with join of two edges tables, and two neighbors helper tables.
+	\item {\bf Adamic/Adar (for node)}
+		We used join on the edges table, with the neighbors helper table.
+	\item {\bf Preferential attachment (for node)}
+		We used the topN helper table, just like in the global version.
+	\item {\bf Graph Distance (for node)}
+		We used a recursive procedure, starting with a temporary table with all the node's neighbors,
+		and on each iteration N we added all the neighbors of nodes in depth N-1. This implementation
+		required us to reconfigure MySQL maximum recursion depth.
+	\item {\bf Katz (for node)}
+		We used a recursive procedure to calculate $|P^l(x,y)|$ for all reachable nodes in depth 3,
+		and stored that in a temporary table. We then used that to calculate the score.
+	\item {\bf Rooted PageRank (for node)}
+
 \end{itemize}

### 2013-02-19 article/paper.tex
more on mysql implementation and redis features

@@
 \begin{itemize}
-	\item {\bf Helper Tables} We generated the following helper tables 
-		to speed up some algorithms:
+	\item {\bf Helper Tables} 
+        We generated the following helper tables to speed up some algorithms:
 		\begin{itemize}
@@
 	\item {\bf Rooted PageRank (for node)}
-
+        We used an iterative loop over a temporary table <id, rpr, new-rpr>, initiated with all the 
+        nodes in the graph, and 1/N value where N is the number of nodes in the graph. On every 
+        iteration we updated the new-rpr value, using the formula above. We stopped when the algorithm
+        converged on the top-10 scoring nodes and their order.
 \end{itemize}
@@
 Redis is an open-source, in-memory key-value store database system, sponsored
-by VMware. It's main features are atomic operations, data structure as value
-(hash, list, set and sorted-set), optional persistence, pub/sub mechanism,
-built-in Lua interpreter and master-slave replication.
+by VMware. It's written in C and has atomic operations, we used the following features:
+\begin{itemize}
+	\item {\bf Transactions}
+        You can use redis transaction to save time spent on network trafic 
+        between the client API and the server. We used that feature to speed up
+        the graph load significantly.
+	\item {\bf Data structure as value}
+        Redis support storing many types of data structures as valuse and 
+        performe efficient, atomic operation over them. I.e. there are strings,
+        hashes (key-value pairs), lists, sets (in which we used to store the 
+        adjacency lists), and sorted-sets (like sets, but with rank for each item).
+        Operations include: incrementing value in hash, appending to lists, 
+        union/intersection/difference on sets, and getting sorted-set member with top rank.
+	\item {\bf Lua Scripting}
+        Lua scripting enable you to run your own code, in an atomic matter inside the server.
+        Unlike transactions, you can add non-Redis logic to this atomic operation. We used 
+        Lua scripting to speed-up and algorithem which took long time to run.\footnote{Sara: we are kind of abusing this feature, by locking the db and assuming single client, should we mention that?}
+\end{itemize}
 
@@
 since we couldn't store nodes without neighbors, as redis doesn't allow to
-store empty sets. \#TODO: why doesn't it matter in our case
+store empty sets. This isn't such an issue for us, as all the algorithems we tested
+return an empty set for such nodes, and we still kept a nodes db <id, name> which
+could provide us with the node count (i.e. needed for the Rooted PageRank implementation)
+\linebreak
+Implementation details:
+\begin{itemize}
+	\item {\bf Helper Database} 
+        We only generated one database speed up the Preferential attachment algorithm:
+	    topN (id, number of neighbors), a database which holds 101 nodes with most neighbors.
+	\item {\bf Common Neighbors (global)} 
+        We implemented this algorithm using the Lua scripting feature. TODO
+	\item {\bf Jaccard's Coefficient (global)} 
+	\item {\bf Adamic/Adar (global)} 
+	\item {\bf Preferential attachment (Global)}
+	\item {\bf Common Neighbors (for node)}
+	\item {\bf Jaccard's Coefficient (for node)}
+	\item {\bf Adamic/Adar (for node)}
+	\item {\bf Preferential attachment (for node)}
+	\item {\bf Graph Distance (for node)}
+	\item {\bf Katz (for node)}
+	\item {\bf Rooted PageRank (for node)}
+\end{itemize}
 

### 2013-02-19 article/paper.tex
finished with redis implementation details

@@
 		with it's 'LOAD DATA' statement. From all the systems we tested, this offered 
-		the easiest and fastest to load our graph.
+		the easiest and fastest way to load our graph.
 \end{itemize}
 
-In this case, the algorithms were implemented as a SQL stored-procedures only,
+In this case, the algorithms were implemented as a SQL stored-procedures,
 using indices and intermediate tables when possible. A Python script was used
@@
 \linebreak
+
 Implementation details:
@@
         Unlike transactions, you can add non-Redis logic to this atomic operation. We used 
-        Lua scripting to speed-up and algorithem which took long time to run.\footnote{Sara: we are kind of abusing this feature, by locking the db and assuming single client, should we mention that?}
+        Lua scripting to speed-up and algorithem which took long time to run. \footnote{Sara: 
+        we are kind of abusing this feature, by locking the db and assuming single client, 
+        should we mention that?}
 \end{itemize}
@@
 The graphs were represented using adjacency lists, i.e. a key is a node-id and
-it's value is a set of his neighbors. That implementation posed a limitation,
-since we couldn't store nodes without neighbors, as redis doesn't allow to
-store empty sets. This isn't such an issue for us, as all the algorithems we tested
-return an empty set for such nodes, and we still kept a nodes db <id, name> which
-could provide us with the node count (i.e. needed for the Rooted PageRank implementation)
+it's value is a set of his neighbors. We also kept a nodes database <id, name>, 
+basicall just to get a node count (i.e. needed for the Rooted PageRank implementation),
+because redis can't hold empty sets.
 \linebreak
+
 Implementation details:
@@
 	\item {\bf Common Neighbors (global)} 
-        We implemented this algorithm using the Lua scripting feature. TODO
+        We implemented this algorithm using the Lua scripting feature. First we accumulate 
+        the number of common neighbors for each node pair, then iterated over the results 
+        to keep the top scoring, and return a sorted result.
 	\item {\bf Jaccard's Coefficient (global)}
+        Using Lua scripting we used the first part of the Common Neighbors implementation,
+        and the relation between the cardinality of union and intersection, and that redis
+        can give us the cardinality of a set in a single operation (i.e. number of neighbors)
+        we calculated the score and continued similarly to the above implementation.
 	\item {\bf Adamic/Adar (global)} 
+        Using the Lua scripting, we accumulated list of common neighbors for each pair,
+        then went over that list and calculated the algorithm, keeping only the top scoring pairs.
 	\item {\bf Preferential attachment (Global)}
+        We used the helper database that we created beforehand, to find pairs with maximal product.
 	\item {\bf Common Neighbors (for node)}
+        We used the same logic as with the global implementation, but with the Python API,
+        as it was fast enough.
 	\item {\bf Jaccard's Coefficient (for node)}
+        We used the same logic as with the global implementation, but with the Python API,
+        as it was fast enough.
 	\item {\bf Adamic/Adar (for node)}
+        We used the same logic as with the global implementation, but with the Python API,
+        as it was fast enough.
 	\item {\bf Preferential attachment (for node)}
+        We used the same logic as with the global implementation.
 	\item {\bf Graph Distance (for node)}
+        Using the Python API and an iterative loop, we started with the source node 
+        as depth 0, on each iteration we expended all the nodes from the previous depth.
 	\item {\bf Katz (for node)}
+        Using Lua, we started by calculating the $|P^l(x,y)|$ for all reachable nodes in depth 3,
+        and then used that to calculate the score.
 	\item {\bf Rooted PageRank (for node)}
+        Using Lua, we used an iterative loop over a temporary table <id, rpr, new-rpr>, initiated with all the 
+        nodes in the graph, and 1/N value where N is the number of nodes in the graph. On every 
+        iteration we updated the new-rpr value, using the formula above. We stopped when the algorithm
+        converged on the top-10 scoring nodes and their order.
 \end{itemize}
@@
 Neo4J is a multi-platform, open-source, graph database supported by Neo
-Technology. It features full ACID transactions, expressive graph query
+Technology. Some of it's main features are:
+\begin{itemize}
+    \item {\bf transactions}
+        Neo4J supports ACID transactions, similar to RDBMS. This also enables 
+        you to send chunk of commands to the database instead of single 
+        instactions and avoid network latency for each call. We tried to use
+        this to load our graph, but this method is just too slow for bulk insertions.
+    \item {\bf Embedded mode}
+        Embedding Neo4J in your application, mainly saves time on REST calls 
+        and enables fast interaction with the database. We used that feature 
+        to load the graph, and the move the generated files to the server.
+        We found that currently, this is the fastest way to bulk insert a 
+        large graph to Neo4J.
+    \item {\bf Cypher query language}
+        Cypher is a declerative query language for graphs, enabling you to
+        match pattern, filter on properties and make changes. It's syntax is
+        much like SQL, e.g. friends of friends which are not directly connected:
+        \begin{verbatim}
+            START n=node(...)
+            MATCH n-->m-->o
+            WHERE not ( n-->o )
+            RETURN o
+        \end{verbatim}
+    \item {\bf Lucene Indexing}
+\end{itemize}
+ACID transactions, expressive graph query
 language, indexing and high availability. It can operate in an embedded or

### 2013-02-23 article/paper.tex
added Neo4J implementation details, and data-sets information

@@
 These databases are all open-source, enabling us to publish these benchmarks,
-and popular in their domain, therefore considered as a viable option for such social network implementation.
+and popular in their domain, therefore considered as a viable option for 
+such social network implementation.
 
@@
 		\[{|N(x) \cup N(y)|} = {|N(x)| + |N(y)| - |N(x) \cap N(y)|}\]
-		So to calculate the score we used the common-neighbors-count and the neighbors helper tables.
+		So to calculate the score we used the common-neighbors-count and 
+		the neighbors helper tables.
 	\item {\bf Adamic/Adar (global)} 
@@
 	\item {\bf Graph Distance (for node)}
-		We used a recursive procedure, starting with a temporary table with all the node's neighbors,
-		and on each iteration N we added all the neighbors of nodes in depth N-1. This implementation
-		required us to reconfigure MySQL maximum recursion depth.
+		We used a recursive procedure, starting with a temporary table with all 
+		the node's neighbors, and on each iteration N we added all the neighbors 
+		of nodes in depth N-1. This implementation required us to reconfigure 
+		MySQL maximum recursion depth.
 	\item {\bf Katz (for node)}
-		We used a recursive procedure to calculate $|P^l(x,y)|$ for all reachable nodes in depth 3,
-		and stored that in a temporary table. We then used that to calculate the score.
+		We used a recursive procedure to calculate $|P^l(x,y)|$ for all reachable 
+		nodes in depth 3, and stored that in a temporary table. We then used that 
+		to calculate the score.
 	\item {\bf Rooted PageRank (for node)}
-        We used an iterative loop over a temporary table <id, rpr, new-rpr>, initiated with all the 
-        nodes in the graph, and 1/N value where N is the number of nodes in the graph. On every 
-        iteration we updated the new-rpr value, using the formula above. We stopped when the algorithm
+        We used an iterative loop over a temporary table <id, rpr, new-rpr>, 
+		initiated with all the nodes in the graph, and 1/N value where N is the 
+		number of nodes in the graph. On every iteration we updated the 
+		new-rpr value, using the formula above. We stopped when the algorithm
         converged on the top-10 scoring nodes and their order.
@@
         Unlike transactions, you can add non-Redis logic to this atomic operation. We used 
-        Lua scripting to speed-up and algorithem which took long time to run. \footnote{Sara: 
+        Lua scripting to speed-up and algorithm which took long time to run. \footnote{Sara: 
         we are kind of abusing this feature, by locking the db and assuming single client, 
@@
 	\item {\bf Preferential attachment (Global)}
-        We used the helper database that we created beforehand, to find pairs with maximal product.
+        We used the helper database that we created beforehand, to find pairs 
+		with maximal product.
 	\item {\bf Common Neighbors (for node)}
-        We used the same logic as with the global implementation, but with the Python API,
-        as it was fast enough.
+        We used the same logic as with the global implementation, but with the 
+		Python API, as it was fast enough.
 	\item {\bf Jaccard's Coefficient (for node)}
-        We used the same logic as with the global implementation, but with the Python API,
-        as it was fast enough.
+        We used the same logic as with the global implementation, but with the 
+		Python API, as it was fast enough.
 	\item {\bf Adamic/Adar (for node)}
-        We used the same logic as with the global implementation, but with the Python API,
-        as it was fast enough.
+        We used the same logic as with the global implementation, but with the 
+		Python API, as it was fast enough.
 	\item {\bf Preferential attachment (for node)}
@@
 	\item {\bf Graph Distance (for node)}
-        Using the Python API and an iterative loop, we started with the source node 
-        as depth 0, on each iteration we expended all the nodes from the previous depth.
+        Using the Python API and an iterative loop, we started with the source 
+		node as depth 0, on each iteration we expended all the nodes from the 
+		previous depth.
 	\item {\bf Katz (for node)}
-        Using Lua, we started by calculating the $|P^l(x,y)|$ for all reachable nodes in depth 3,
-        and then used that to calculate the score.
+        Using Lua, we started by calculating the $|P^l(x,y)|$ for all reachable 
+		nodes in depth 3, and then used that to calculate the score.
 	\item {\bf Rooted PageRank (for node)}
-        Using Lua, we used an iterative loop over a temporary table <id, rpr, new-rpr>, initiated with all the 
-        nodes in the graph, and 1/N value where N is the number of nodes in the graph. On every 
-        iteration we updated the new-rpr value, using the formula above. We stopped when the algorithm
-        converged on the top-10 scoring nodes and their order.
+        Using Lua, we used an iterative loop over a temporary 
+		table <id, rpr, new-rpr>, initiated with all the nodes in the graph, 
+		and 1/N value where N is the number of nodes in the graph. On every 
+        iteration we updated the new-rpr value, using the formula above. 
+		We stopped when the algorithm converged on the top-10 scoring nodes 
+		and their order.
 \end{itemize}
@@
 \begin{itemize}
-    \item {\bf transactions}
+    \item {\bf Transactions}
         Neo4J supports ACID transactions, similar to RDBMS. This also enables 
@@
     \item {\bf Embedded mode}
-        Embedding Neo4J in your application, mainly saves time on REST calls 
+        Embedding Neo4J in your application mainly saves time on REST calls 
         and enables fast interaction with the database. We used that feature 
-        to load the graph, and the move the generated files to the server.
+        to load the graph, and then move the generated files to the server.
         We found that currently, this is the fastest way to bulk insert a 
-        large graph to Neo4J.
+        large graph into a Neo4J server.
     \item {\bf Cypher query language}
@@
         \end{verbatim}
-    \item {\bf Lucene Indexing}
+    \item {\bf Indexing}
+		There are two main indexing options in Neo4J:
+		\begin{enumerate}
+			\item {\bf Using the graph}
+				An index can be implemented as a layed over the graph, 
+				i.e. by adding more relations which represent the index
+				structure.
+			\item {\bf Separate index}
+				By default, Neo4J uses Apache Lucene as a backend index engine.
+				This enables you to index Nodes and Relations, and use all Lucene's
+				features, including fulltext index.
+				We used this form of indexing to speed-up the Preferential attachment
+				algorithm.
+		\end{enumerate}
 \end{itemize}
-ACID transactions, expressive graph query
-language, indexing and high availability. It can operate in an embedded or
-client-server architecture.
 
-In this database, we attempted to use only Neo4j's declarative query language
-(Cypher) to implement the algorithms, and the client-server architecture to run
-them with. The benchmarking was performed using the Python API, which also
-assisted in implementing some multi-query algorithms. We found that the best
-way to load the graph into Neo4J was to use the BatchInserter class in the
-embedded architecture, and copy the created files into the server.
+We attempted to implement all the algorithms using Cypher. Though this was 
+usually an easy task, some of the language current limitations prevented us 
+from achiving that goal:
+\begin{itemize}
+	\item Lack of major math functions (e.g. Power, Log, Rand), and no support 
+		for user defined function, prevented from implementing the Adamic/Adar 
+		algorithm or to use multiple queries, joined by logic in Python, 
+		to implement the Katz algorithm.
+	\item Performance issues on mutiple start nodes, in particular when matching
+		a non-trivial pattern over the whole graph (i.e. our global benchmarks).
+		We had to omit the global version of Jaccard Coefficient, and find another
+		approach to the global Common Neighbors implementation.
+\end{itemize}
 
-There are some limitations to the Cypher language users should be aware of:
+Implementation details:
 \begin{itemize}
-\item There are not many built in functions (e.g. no Power, Log, or Rand
-  functions) 
-\item No support for user defined functions
-\item Queries are really slow when matching a non-trivial pattern over the whole
-graph (e.g. common neighbors)  
+	\item {\bf Helper Neighbor count property}
+		Since Neo4J doen't provide a fast way to get the number of node's neighbors,
+		we added a neighbor count property to each node. This was useful for 
+		almost any algorithm we implemented.
+	\item {\bf Helper Index}
+		We generated an Lucene index containing 101 nodes with most neighbors,
+		to speed up the Preferential attachment algorithm.
+	\item {\bf Common Neighbors (global)} 
+		In order to circumvent a Cypher performance issue with multiple start 
+		nodes, we used a different approach to the Common Neighbors implementation:
+		we realized that the result-set of such query will only contain nodes with
+		at least $\alpha$ number of neighbors, where $\alpha$ is number of neighbors
+		of the lowers scoring pair in the result-set.
+		So we used a binary search method to find that $\alpha$, by iteratively 
+		running the	query over nodes with $\beta$ number of neighbors, where $\beta$
+		is initiated to $M/2$ ($M$ is the maximum number of neighbors a node in the
+		graph has), divding $\beta$ by two each iteration, until $\alpha > \beta$.
+	\item {\bf Preferential attachment (Global)}
+        We used the helper index that we created beforehand, to find pairs with 
+		maximal product.
+	\item {\bf Common Neighbors (for node)}
+        We used a simple query.
+	\item {\bf Jaccard's Coefficient (for node)}
+        We used a simple query, using the relation between the cardinality of 
+		union and intersection
+	\item {\bf Preferential attachment (for node)}
+        We used the helper index that we created beforehand, to find pairs with 
+		maximal product.
+	\item {\bf Graph Distance (for node)}
+		We iteratively ran a query, returning nodes until depth $i$ (increased on 
+		every iteration), until depth limit or returend data set limit has met.
+	\item {\bf Katz (for node)}
+		Without power function support in Cypher, we had to use multiple queries,
+		to calculate the Katz algorithm.
+	\item {\bf Rooted PageRank (for node)}
+        We used an iterative loop with the same logic like the other two databases,
+		storing the intermediate values as node properties.
 \end{itemize}
@@
 \begin{itemize}
-\item Three graphs were extracted from the DBLP XML records using the authors as
-nodes, and co-authorship relation as edges. Each graph was over a different
-time period, and  we only kept authors with 3 or more publication within the
-selected time period (core-3).
+	\item 
+		Three graphs were extracted from the DBLP XML records using the authors 
+		as nodes, and co-authorship relation as edges. Each graph was over a 
+		different time period, and  we only kept authors with 3 or more 
+		publication within the selected time period (core-3). 
+	\item 
+		Seven graphs from the Stanford Network Analysis Project (SNAP) dataset
+		collection:
+		\begin{enumerate}
+			\item {ego-Facebook} 
+				Anonymized Facebook data that was collected from survey 
+				participants using a Facebook app.
+			\item {email-Enron} 
+				Enron email communication network, released by the 
+				Federal Energy Regulatory Commission during its investigation.
+			\item {ca-AstroPh}
+				Scientific collaborations between authors papers submitted to 
+				Astro Physics category.
+			\item {ca-CondMat}
+				Scientific collaborations between authors papers submitted to 
+				Condense Matter category.
+			\item {ca-GrQc}
+				Scientific collaborations between authors papers submitted to 
+				General Relativity and Quantum Cosmology category.
+			\item {ca-HepPh}
+				Scientific collaborations between authors papers submitted to 
+				High Energy Physics - Phenomenology category.
+			\item {ca-HepTh}
+				Scientific collaborations between authors papers submitted to 
+				High Energy Physics - Theory category
+		\end{enumerate}
+\end{itemize}
 
-\item Seven graphs from the Stanford Network Analysis Project (SNAP) dataset
-  collection. No changes were made to these graphs.
-\end{itemize}
+\begin{tabular}{ |l||c|r| }
+	\hline
+	Data-set & Node Count & Edge Count \\
+	\hline
+	dblp-2002-2009-core3 & 182493 & 1621846 \\
+	dblp-2010-2012-core3 & 248695 & 2589320 \\
+	dblp-all-core3       & 366600 & 4349796 \\
+	ego-Facebook         & 4039   & 170174  \\
+	email-Enron          & 36692  & 367662  \\
+	ca-AstroPh           & 18771  & 396160  \\
+	ca-CondMat           & 23133  & 186936  \\
+	ca-GrQc              & 5241   & 28980   \\
+	ca-HepPh             & 12006  & 237010  \\
+	ca-HepTh             & 9875   & 51971   \\
+	\hline  
+\end{tabular}
 
